Burning sage: Reversing the curse of dimensionality in the visualization of high-dimensional data

### 2021-07-26 paper/paper.Rmd
fixed pre-processing consistent spelling

## Data preprocessing {#sec:prep}

Before applying the transformation, it can be important to preprocess the data, as is generally required with methods for the visualisation of high-dimensional data. In particular, when working with projections that combine multiple variables it is important to ensure a common scale across the dimensions. This is especially important with the sage display, where the overall scale (set by the maximum radius $R$) determines the effect of the transformation. Scaling is commonly also combined with centering as a preprocessing step. This is less important in our implementation because we always center the projected data before applying our transformation (i.e. the projected mean defines the origin of our polar coordinate system in the plane). Centering and scaling together would be achieved by standardizing each variable in the data to be centered at 0 and have a variance equal to 1.

>>>>

## Data pre-processing {#sec:prep}

Before applying the transformation, it can be important to pre-process the data, as is generally required with methods for the visualisation of high-dimensional data. In particular, when working with projections that combine multiple variables it is important to ensure a common scale across the dimensions. This is especially important with the sage display, where the overall scale (set by the maximum radius $R$) determines the effect of the transformation. Scaling is commonly also combined with centering as a pre-processing step. This is less important in our implementation because we always center the projected data before applying our transformation (i.e. the projected mean defines the origin of our polar coordinate system in the plane). Centering and scaling together would be achieved by standardizing each variable in the data to be centered at 0 and have a variance equal to 1.

### 2021-07-26 paper/paper.tex
fixed pre-processing consistent spelling

\hypertarget{sec:prep}{%
\subsection{Data preprocessing}\label{sec:prep}}

Before applying the transformation, it can be important to preprocess
the data, as is generally required with methods for the visualisation of
high-dimensional data. In particular, when working with projections that
combine multiple variables it is important to ensure a common scale
across the dimensions. This is especially important with the sage
display, where the overall scale (set by the maximum radius \(R\))
determines the effect of the transformation. Scaling is commonly also
combined with centering as a preprocessing step. This is less important
in our implementation because we always center the projected data before
applying our transformation (i.e.~the projected mean defines the origin
of our polar coordinate system in the plane). Centering and scaling
together would be achieved by standardizing each variable in the data to
be centered at 0 and have a variance equal to 1.

>>>>

\hypertarget{sec:prep}{%
\subsection{Data pre-processing}\label{sec:prep}}

Before applying the transformation, it can be important to pre-process
the data, as is generally required with methods for the visualisation of
high-dimensional data. In particular, when working with projections that
combine multiple variables it is important to ensure a common scale
across the dimensions. This is especially important with the sage
display, where the overall scale (set by the maximum radius \(R\))
determines the effect of the transformation. Scaling is commonly also
combined with centering as a pre-processing step. This is less important
in our implementation because we always center the projected data before
applying our transformation (i.e.~the projected mean defines the origin
of our polar coordinate system in the plane). Centering and scaling
together would be achieved by standardizing each variable in the data to
be centered at 0 and have a variance equal to 1.
